Hijacking Malaria Simulators with Probabilistic Programming

### 2019-05-26 paper/icml_ai4good/main.tex
updated;

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2019}
\newcommand{\bg}[1]{~{{[{\it \textcolor{red}{{\bf BG:} #1}}]}}}
\newcommand{\cs}[1]{~{{[{\it \textcolor{red}{{\bf CS:} #1}}]}}}
\newcommand{\ag}[1]{~{{[{\it \textcolor{red}{{\bf AG:} #1}}]}}}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2019}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes, arrows.meta}
\tikzset{
  shift left/.style ={commutative diagrams/shift left={#1}},
  shift right/.style={commutative diagrams/shift right={#1}}
}
\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
            base/.style = {rectangle, rounded corners, draw=black,
                           minimum width=4cm, minimum height=1cm,
                           text centered, font=\sffamily},
  activityStarts/.style = {base, fill=blue!50},
       startstop/.style = {base, fill=red!50},
    activityRuns/.style = {base, fill=green!50},
         process/.style = {base, minimum width=2.5cm, fill=orange!55,
                           font=\ttfamily},
}
\makeatletter
\tikzset{join/.code=\tikzset{after node path={%
\ifx\tikzchainprevious\pgfutil@empty\else(\tikzchainprevious)%
edge[every join]#1(\tikzchaincurrent)\fi}}}
\makeatother
%
\tikzset{>=stealth',every on chain/.append style={join},
         every join/.style={->}}
\tikzstyle{labeled}=[execute at begin node=$\scriptstyle,
   execute at end node=$]
% The \icmltitle you define below is probably too long as aer.
% Therefore, a short form for the running title is supplied here:
%\icmltitlerunning{Hijacking Simulators for the Greater Good}
\icmltitlerunning{Hijacking Malaria Simulators
	with Probabilistic Programming}

@@

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{equal,to}
\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
\icmlauthor{Cieua Vvvvv}{goo}
\icmlauthor{Iaesut Saoeu}{ed}
\icmlauthor{Fiuea Rrrr}{to}
\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
\icmlauthor{Aaoeu Iasoh}{goo}
\icmlauthor{Buiui Eueu}{ed}
\icmlauthor{Aeuia Zzzz}{ed}
\icmlauthor{Bieea C.~Yyyy}{to,goo}
\icmlauthor{Teoau Xxxx}{ed}
\icmlauthor{Eee Pppp}{ed}
\end{icmlauthorlist}

\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

@@

\section{Introduction}
Ending the epidemics of AIDS, tuberculosis, malaria and other infectious diseases by 2030 is a key target within the Good Health \& Well-Being section of the UN Sustainable Development Goals \cite{refugees_2030,un_sustainable2018}. 
However, despite decades of substantial international efforts, these diseases kill hundreds of million people a year.
For example, malaria still annually kills about a quarter of a million children under the age of 5 in Africa alone.

@@

This paper first gives an overview of existing Malaria simulators (Section \ref{sec:background}), and proceed by introducing the necessary background on the \textit{pyprob} framework and the concept of universal probabilistic programming (Section \ref{sec:hijackingsimulators}). Our approach is then demonstrated and analysed in the context of a Malaria case study (Section \ref{sec:casestudy}).

@@

In-silico simulators have become a crucial tool in evidence-based decision-making within a large number of disciplines, including statistical physics~\cite{landau_binder_2014}, financial modeling~\cite{jackel2002monte},
weather prediction~\cite{evensen1994sequential}, epidemiology~\cite{smith2008towards} and many others.
In many cases, simulation output can augment or even replace real data that may otherwise be costly or even impossible to generate.
Recent advances in hardware have enabled simulations to model increasingly complex systems.
Epidemiology studies the prevalence and spreading of diseases across populations. Recent advances in hardware have enabled simulations to model the dynamics of infectious diseases, such as Malaria, in ever greater detail.

@@

Two the most advanced Malaria simulators, namely EMOD~\cite{bershteyn2018implementation} and OpenMalaria  \cite{smith2008towards}, have proven to be particularly valuable to policymakers.
OpenMalaria is based on microsimulations of Plasmodium falciparum in humans and was originally developed to simulate the impacts of malaria vaccines within simple villages or districts
Compared with OpenMalaria, EMOD is able to simulate a variety of additional drivers, including complex geographies complete with migration and a large number of policy interventions
Both EMOD and OpenMalaria are open source and implemented in C++.

@@

 Probabilistic programming~\cite{gordon2014probabilistic,staton2016semantics,kozen1979semantics} 
can be used to express probabilistic models and consequently perform automated inference these. Once a probabilistic model has been expressed in a probabilistic programming language, a wide range of inference techniques, such as Markov Chain Monte Carlo (MCMC)\cite{}, Variational Inference~(VI)\cite{} and Deep Neural Networks~(DNN)\cite{},  can be used by non-experts in an automated fashion.

@@

Finally, the entry point to the simulator, i.e. \textit{main} in C++, is replaced by a special \textit{forward} call, in this case \textit{pyprob\_cpp::forward}.
This allows the PPS to generate rollouts from the simulator remotely.

@@

\begin{figure}
\centering
 \scalebox{.5}{
\begin{tikzpicture}[node distance=1.5cm,
    every node/.style={fill=white, font=\sffamily}, align=center]
  % Specification of nodes (position, etc.)
  % \node (start)             [activityStarts]              {Activity starts};
  \node (SimulatorSystem)     [activityStarts]          {Simulator System \\ e.g. EMOD};
   \node (randomprim)      [process, left of=SimulatorSystem, xshift=5.6cm]
                                                      {Redefine RNG \\ to make \\ externally \\ callable};
  \node (onStartBlock)      [process, below of=SimulatorSystem]   {Specify Model \\ e.g. XML files};
  \node (activityRuns)      [activityRuns, below of=onStartBlock]
                                                      {Run Simulator};
  \node (onPauseBlock)      [startstop, below of=activityRuns, yshift=-1cm]
                                                                {Posterior Output};
  % \node (onStopBlock)       [process, below of=onPauseBlock, yshift=-1cm]
  %                                                                {};
  % \node (onDestroyBlock)    [process, below of=onStopBlock, yshift=-1cm] 
  %                                                             {onDestroy()};
  \node (onRestartBlock)    [process, right of=activityRuns, xshift=3cm]
                                                              {PPS hijacks \\ random number \\ generator};
  \node (ActivityEnds)      [startstop, below of=onRestartBlock, yshift=-1cm]
                                                        {Result summaries \\ path probabilities};
  % \node (ActivityDestroyed) [startstop, below of=onDestroyBlock]
  %                                                   {Activity is shut down};     
  % Specification of lines between nodes specified above
  % with aditional nodes for description 
  % \draw[->]             (start) -- (onCreateBlock);
  \draw[->]     (SimulatorSystem) -- (onStartBlock);
  \draw[dashed, <-]  (SimulatorSystem) -- (randomprim);
  % \draw[->]      (onStartBlock) -- (onResumeBlock);
  \draw[->]     (onStartBlock) -- (activityRuns);
  \draw[->]      (activityRuns) -- (onPauseBlock);
  % \draw[->]      (onPauseBlock) -- node {The activity is no longer visible}
  %                                  (onStopBlock);
  % \draw[->]       (onStopBlock) -- node {The activity is shut down by
  %                                  user or system} (onDestroyBlock);
  % \draw[->]    (onRestartBlock) -- (activityRuns);
  \path[->, shift left=.75ex]
  (onRestartBlock) edge (activityRuns)
  (activityRuns) edge (onRestartBlock);
  % \draw[<-]    (activityRuns) -- (onRestartBlock);
  % \draw[->]       (onStopBlock) -| node[yshift=1.25cm, text width=3cm]
  %                                  {The activity comes to the foreground}
  %                                  (onRestartBlock);

  \draw[->]    (onRestartBlock) -- (ActivityEnds);
  % \draw[->]      (onPauseBlock) -| node(priorityXMemory)
  %                                  {todo}
  %                                  (ActivityEnds);
  % \draw           (onStopBlock) -| (priorityXMemory);
  % \draw[->]     (ActivityEnds)  |- node [yshift=-2cm, text width=3.1cm]
  %                                   {User navigates back to the activity}
  %                                   (SimulatorSystem);
  % \draw[->] (onPauseBlock.east) -- ++(2.6,0) -- ++(0,2) -- ++(0,2) --                
  %    node[xshift=1.2cm,yshift=-1.5cm, text width=2.5cm]
  %    {The activity comes to the foreground}(onResumeBlock.east);
  \end{tikzpicture}
  }
  \label{fig:how}
  \caption{This flow-chart provides an overview of the process of how our system hijacks a generic population-based epidemiology simulator, such as EMOD, and how we modify the simulator to 
  to hijack the random number generator (RNG).}
  \end{figure}

@@

Ensemble methods are commonly used in statistics in order to combine the predictive power of multiple models \cite{cameron2015defining,smith_ensemble_2012}. To this end, recent work has attempted to characterise the similarities and differences between two of the most advanced Malaria epidemiology simulators, EMOD \cite{bershteyn2018implementation} and OpenMalaria \cite{smith2008towards}. Evaluation is usually done by comparing a number of output parameters across a range of hand-crafted standard scenarios reflecting different geographical locations across Africa~\cite{smith_ensemble_2012}.

In the following, we illustrate how our method introduces a novel introspection paradigm. By extracting trace graphs from population-based simulators, policymakers can ask specific questions about properties of the model trace flow.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth/2]{../plots/EIR_Ifakara.pdf}
	\caption{Seasonal Entomological Inoculation Rate (EIR) for the Ifakara scenario. Data is averaged over $30$ day periods.}
	\label{fig:EIR}
\end{figure}

@@

Additionally, by associating nodes in trace graphs representing the same physical processes within different models, the significance of model detail can be evaluated. For example, the full trace presented in Table \ref{table:asingleaddress} represent a sampling step associated with within-host dynamics of the Malaria parasite \textit{Falciparum} in OpenMalaria node $A1$. The same physical process also occurs in EMOD's trace graph at position $A7$ (see Section \ref{table:addresses}).
Comparisons like these could help developers better control model complexity, and even provide an alternative testing and debugging paradigm.

@@

\begin{table}[h!]
\footnotesize
  \setlength{\tabcolsep}{1mm}
\label{table:asingleaddress}
  \caption{An example of an address generated for the model run in the OpenMalaria simulator. We can see that A1
  relates to Generating a member of the human population who may or may not be infect with the Malaria disease. We get something similar for EMOD, except this relates to A7 in the EMOD program execution.}
  \def\arraystretch{1.25}
  % \setlength{\tabcolsep}{1mm}
  \begin{tabularx}{0.46\textwidth}{@{}lX@{}l@{}} 
    \toprule
    Address ID & Full address \\
    \midrule
  A1 & [forward()+0x204; OM::Simulator::

@@

In this work we have demonstrated a method 
that enables one to hijack populationbased simulators, extending 
the work of \citep{baydin2018efficient}. 
We applied our method to two Malaria orientated population-based simulators and 
generated a variety of trace graphs.
Finally, we have shown how our system
enables policy makers and non-experts to analyse simulator outputs in a 
way previously unavailable in the field of epidemiology.

To extend our work further we aim to implement additional 
tools that will facilitate complicated inference procedures that condition on simulator 
output. We will also evaluate additional scenarios across Africa and South-East Asia to better understand the similarities and differences between EMOD and OpenMalaria.

\quad\\
\quad\\

>>>>

% Use the following line for the initial blind version submitted for review:
% \usepackage{icml2019}
\newcommand{\bg}[1]{~{{[{\it \textcolor{red}{{\bf BG:} #1}}]}}}
\newcommand{\cs}[1]{~{{[{\it \textcolor{red}{{\bf CS:} #1}}]}}}
\newcommand{\ag}[1]{~{{[{\it \textcolor{red}{{\bf AG:} #1}}]}}}
% If accepted, instead use the following line for the camera-ready submission:
\usepackage[accepted]{icml2019}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes, arrows.meta}
\tikzset{
  shift left/.style ={commutative diagrams/shift left={#1}},
  shift right/.style={commutative diagrams/shift right={#1}}
}
\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
            base/.style = {rectangle, rounded corners, draw=black,
                           minimum width=4cm, minimum height=1cm,
                           text centered, font=\sffamily},
  activityStarts/.style = {base, fill=blue!50},
       startstop/.style = {base, fill=red!50},
    activityRuns/.style = {base, fill=green!50},
         process/.style = {base, minimum width=2.5cm, fill=orange!55,
                           font=\ttfamily},
}
\makeatletter
\tikzset{join/.code=\tikzset{after node path={%
\ifx\tikzchainprevious\pgfutil@empty\else(\tikzchainprevious)%
edge[every join]#1(\tikzchaincurrent)\fi}}}
\makeatother
%
\tikzset{>=stealth',every on chain/.append style={join},
         every join/.style={->}}
\tikzstyle{labeled}=[execute at begin node=$\scriptstyle,
   execute at end node=$]
% The \icmltitle you define below is probably too long as aer.
% Therefore, a short form for the running title is supplied here:
%\icmltitlerunning{Hijacking Simulators for the Greater Good}
\icmltitlerunning{Hijacking Malaria Simulators
	with Probabilistic Programming}

@@

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
% \icmlsetsymbol{equal}{*}

% \begin{icmlauthorlist}
% \icmlauthor{Bradley.~J Gram-Hansen}{equal,en}
% \icmlauthor{Christian Schroeder de Witt}{equal,en}
% \icmlauthor{Tom Rainforth}{st}
% \icmlauthor{Phil H.S. Torr}{eng}
% \icmlauthor{Yee Whye Teh}{st}
% \icmlauthor{At\i{}l\i{}m G\"{u}ne\c{s} Baydin}{eng}
% \end{icmlauthorlist}

% \icmlcorrespondingauthor{Bradley.~J Gram-Hansen}{bradley@robots.ox.ac.uk}
% \icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Bradley.~J Gram-Hansen}{equal,en}
\icmlauthor{Christian Schr\"{o}der de Witt}{equal,en}
\icmlauthor{Tom Rainforth}{st}
\icmlauthor{Phil H.S. Torr}{en}
\icmlauthor{Yee Whye Teh}{st}
\icmlauthor{At\i{}l\i{}m G\"{u}ne\c{s} Baydin}{en}
\end{icmlauthorlist}

\icmlcorrespondingauthor{Bradley.~J Gram-Hansen}{bradley@robots.ox.ac.uk}

\icmlaffiliation{en}{Department of Engineering, University of Oxford, UK}
\icmlaffiliation{st}{Department of Statistics, University of Oxford, UK}

@@

\section{Introduction}
Ending the epidemics of AIDS, tuberculosis, malaria and other infectious diseases by 2030 is a key target within the Good Health \& Well-Being section of the UN Sustainable Development Goals \cite{unitednations,un_sustainable2018}. 
However, despite decades of substantial international efforts, these diseases kill hundreds of million people a year.
For example, malaria still annually kills about a quarter of a million children under the age of 5 in Africa alone.

@@

This paper first gives an overview of existing malaria simulators (Section \ref{sec:background}), and proceed by introducing the necessary background on the \textit{pyprob} framework and the concept of universal probabilistic programming (Section \ref{sec:hijackingsimulators}). Our approach is then demonstrated and analysed in the context of a Malaria case study (Section \ref{sec:casestudy}).

@@

In-silico simulators have become a crucial tool in evidence-based decision-making within a large number of disciplines, including statistical physics~\cite{landau_binder_2014}, financial modeling~\cite{jackel2002monte},
weather prediction~\cite{evensen1994sequential}, epidemiology~\cite{smith2008towards} and many others.
In many cases, simulation output can augment or even replace real data that may otherwise be costly or even impossible to generate.
Recent advances in hardware have enabled simulations to model increasingly complex systems.
Epidemiology studies the prevalence and spreading of diseases across populations. Recent advances in hardware have enabled simulations to model the dynamics of infectious diseases, such as malaria, in ever greater detail.

@@

Two the most advanced malaria simulators, namely EMOD~\cite{bershteyn2018implementation} and OpenMalaria  \cite{smith2008towards}, have proven to be particularly valuable to policymakers.
OpenMalaria is based on microsimulations of \textit{Plasmodium falciparum} in humans and was originally developed to simulate the impacts of malaria vaccines within simple villages or districts
Compared with OpenMalaria, EMOD is able to simulate a variety of additional drivers, including complex geographies complete with migration and a large number of policy interventions
Both EMOD and OpenMalaria are open source and implemented in C++.

@@

 Probabilistic programming~\cite{gordon2014probabilistic,staton2016semantics,kozen1979semantics} 
can be used to express probabilistic models and consequently perform automated inference these. Once a probabilistic model has been expressed in a probabilistic programming language, a wide range of inference techniques, such as Markov Chain Monte Carlo (MCMC)\cite{geyer1992practical}, Black-box Variational Inference~(VI)\cite{ranganath2014black} and amortized inference\cite{le2016inference},  can be used by non-experts in an automated fashion.

@@

Finally, the entry point to the simulator, i.e. \textit{main} in C++, is replaced by a special \textit{forward} call, in this case \textit{pyprob\_cpp::forward}.
This allows the PPS to generate rollouts from the simulator remotely. A pictorial overview of this process is depicted in Figure~\ref{fig:how}.

@@

\begin{figure}
\centering
%  \scalebox{.5}{
% \begin{tikzpicture}[node distance=1.5cm,
%     every node/.style={fill=white, font=\sffamily}, align=center]
%   % Specification of nodes (position, etc.)
%   % \node (start)             [activityStarts]              {Activity starts};
%   \node (SimulatorSystem)     [activityStarts]          {Simulator System \\ e.g. EMOD};
%    \node (randomprim)      [process, left of=SimulatorSystem, xshift=5.6cm]
%                                                       {Redefine RNG \\ to make \\ externally \\ callable};
%   \node (onStartBlock)      [process, below of=SimulatorSystem]   {Specify Model \\ e.g. XML files};
%   \node (activityRuns)      [activityRuns, below of=onStartBlock]
%                                                       {Run Simulator};
%   \node (onPauseBlock)      [startstop, below of=activityRuns, yshift=-1cm]
%                                                                 {Posterior Output};
%   % \node (onStopBlock)       [process, below of=onPauseBlock, yshift=-1cm]
%   %                                                                {};
%   % \node (onDestroyBlock)    [process, below of=onStopBlock, yshift=-1cm] 
%   %                                                             {onDestroy()};
%   \node (onRestartBlock)    [process, right of=activityRuns, xshift=3cm]
%                                                               {PPS hijacks \\ random number \\ generator};
%   \node (ActivityEnds)      [startstop, below of=onRestartBlock, yshift=-1cm]
%                                                         {Result summaries \\ path probabilities};
%   % \node (ActivityDestroyed) [startstop, below of=onDestroyBlock]
%   %                                                   {Activity is shut down};     
%   % Specification of lines between nodes specified above
%   % with aditional nodes for description 
%   % \draw[->]             (start) -- (onCreateBlock);
%   \draw[->]     (SimulatorSystem) -- (onStartBlock);
%   \draw[dashed, <-]  (SimulatorSystem) -- (randomprim);
%   % \draw[->]      (onStartBlock) -- (onResumeBlock);
%   \draw[->]     (onStartBlock) -- (activityRuns);
%   \draw[->]      (activityRuns) -- (onPauseBlock);
%   % \draw[->]      (onPauseBlock) -- node {The activity is no longer visible}
%   %                                  (onStopBlock);
%   % \draw[->]       (onStopBlock) -- node {The activity is shut down by
%   %                                  user or system} (onDestroyBlock);
%   % \draw[->]    (onRestartBlock) -- (activityRuns);
%   \path[->, shift left=.75ex]
%   (onRestartBlock) edge (activityRuns)
%   (activityRuns) edge (onRestartBlock);
%   % \draw[<-]    (activityRuns) -- (onRestartBlock);
%   % \draw[->]       (onStopBlock) -| node[yshift=1.25cm, text width=3cm]
%   %                                  {The activity comes to the foreground}
%   %                                  (onRestartBlock);

%   \draw[->]    (onRestartBlock) -- (ActivityEnds);
%   % \draw[->]      (onPauseBlock) -| node(priorityXMemory)
%   %                                  {todo}
%   %                                  (ActivityEnds);
%   % \draw           (onStopBlock) -| (priorityXMemory);
%   % \draw[->]     (ActivityEnds)  |- node [yshift=-2cm, text width=3.1cm]
%   %                                   {User navigates back to the activity}
%   %                                   (SimulatorSystem);
%   % \draw[->] (onPauseBlock.east) -- ++(2.6,0) -- ++(0,2) -- ++(0,2) --                
%   %    node[xshift=1.2cm,yshift=-1.5cm, text width=2.5cm]
%   %    {The activity comes to the foreground}(onResumeBlock.east);
%   \end{tikzpicture}
% }
   \includegraphics[width=0.45\textwidth]{../plots/system.pdf}
  \label{fig:how}
  \caption{This flow-chart provides an overview of the process of how our we hijack a generic population-based epidemiology simulator, such as OpenMalaria, and how we modify the simulator to 
  to hijack the random number generator (RNG). It demonstrates how information is exchanged between the simulator and the PPS. Green represents events linked to the simulator, purple corresponds to 
  events occurring in the PPS and brown represents an external processes.}
\end{figure}

@@

Ensemble methods are commonly used in statistics in order to combine the predictive power of multiple models \cite{cameron2015defining,smith_ensemble_2012}. To this end, recent work has attempted to characterise the similarities and differences between two of the most advanced malaria epidemiology simulators, EMOD \cite{bershteyn2018implementation} and OpenMalaria \cite{smith2008towards}. Evaluation is usually done by comparing a number of output parameters across a range of hand-crafted standard scenarios reflecting different geographical locations across Africa~\cite{smith_ensemble_2012}.

In the following, we illustrate how our method introduces a novel introspection paradigm. By extracting trace graphs from population-based simulators, policymakers can ask specific questions about properties of the model trace flow
and not just the outcomes of the model, thus providing additional interpretability to the decision making process.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth/2]{../plots/EIR_Ifakara.pdf}
  \vspace{-20pt}
	\caption{Seasonal Entomological Inoculation Rate (EIR) for the Ifakara scenario. Data is averaged over $30$ day periods.}
	\label{fig:EIR}
  \vspace{-10pt}
\end{figure}

@@

Additionally, by associating nodes in trace graphs representing the same physical processes within different models, the significance of model detail can be evaluated. For example, the full trace presented in Table \ref{table:asingleaddress} represent a sampling step associated with within-host dynamics of the malaria parasite \textit{Falciparum} in OpenMalaria node $A1$. The same physical process also occurs in EMOD's trace graph at position $A7$ (see Section \ref{table:addresses}).
Comparisons like these could help developers better control model complexity, and even provide an alternative testing and debugging paradigm.

@@

\begin{table}[h!]
\footnotesize
  \setlength{\tabcolsep}{1mm}
\label{table:asingleaddress}
  \caption{An example of an address generated for the model run in the OpenMalaria simulator. We can see that A1
  relates to Generating a member of the human population who may or may not be infect with the malaria disease. We get something similar for EMOD, except this relates to A7 in the EMOD program execution.}
  \def\arraystretch{1.25}
  % \setlength{\tabcolsep}{1mm}
  \begin{tabularx}{0.46\textwidth}{@{}lX@{}l@{}} 
    \toprule
    Address ID & Full address \\
    \midrule
  A1 & [forward()+0x204; OM::Simulator::

@@

In this work we have demonstrated a method 
that enables one to hijack population-based simulators, extending 
the work of \citep{baydin2018efficient}. 
We applied our method to two malaria orientated population-based simulators and 
generated a variety of trace graphs.
Finally, we have shown how our system
enables policy makers and non-experts to analyse simulator outputs in a 
way previously unavailable in the field of epidemiology.

To extend our work further we aim to implement additional 
tools that will facilitate complicated inference procedures that condition on simulator 
output. We will also evaluate additional scenarios across Africa and Southeast Asia to better understand the similarities and differences between EMOD and OpenMalaria.

\section{Acknowledgments}
We thank Ewan Cameron of MAP at the Big Data Institute and the OpenMalaria team at the Swiss Tropical Health Institute for their time and help. BGH is supported by the EPRSC Autonomous  Intelligent Machines and Systems grant. CSW  is supported by the project Free the Drones (FreeD) under the Innovation Fund Denmark and Microsoft. YWT’s and TR’s research leading to these results has received funding from the European Research Council under the European Union’s Seventh Framework Programme (FP7/2007-2013) ERC grant agreement no. 617071. AGB and PH are supported by EPSRC/MURI grant EP/N019474/1 and AGB is also supported by Lawrence Berkeley National Lab.
